### 2021-08-25 A methodological framework to enable the roaming agreement digitization: An NLP-based approach/paper.tex
25.08.21.3

\section{Introduction}
The roaming procedure maintain persistent connectivity of the subscribers across different networks and geographical regions. Roaming refers to the capability for a subscriber to access the mobile services offered by the Visited Public Mobile Network (VPMN) via the Home Public Mobile Network (HPMN), when moving out of the coverage range of HPMN \cite{b1}. However, before ensuring persistent connectivity the Mobile Network Operators (MNOs) must reach an agreement regarding the technical, commercial and legal relationships known as the Roaming Agreement (RA).

In order to standardize technical, commercial and legal aspects of RA, the GSM Association broadly outlines the content of such RA in standardized form for its members \cite{b2}. Reference \cite{b3} provides a list of the most commonly used GSMA standards, which can be summarized into: (1) AA.12 constitutes a standard GSMA or Permanent Reference Document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.); (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.) and (4) AA.19 constitutes an addendum to the international RA in order to determine specific properties such as charging, billing, and accounting for a specific scenario like the SMS interworking.

While it is true that it is not mandatory to follow the standards proposed by GSMA, according to authoritative voices in the field of negotiating RA drafting, most MNOs follow them strictly \cite{b4}. Therefore, a first point to consider in the RA drafting is how far it is deviated from the GSMA's proposed standards. Thus, during the drafting process of the agreement, the parties should analyze the sub-articles contained in the standard templates to determine whether:

\begin{enumerate}
\item Leave an article/sub-article as found in the template thereby establishing a standard clause.

@@

\item Specify the value of certain variables that are found in a certain text, such as dates, names of entities, amounts and others

@@

However, a successful RA drafting goes through a complex negotiation process in which, currently the parties, i.e. the Mobile Network Operators (MNOs), still use asynchronous flows such as email or even regular mail for information exchange. Since these processes lack transparency, which can result in the violation of the RA by MNOs, it is necessary to provide a transparent digitization system for RA drafting negotiations. For this reason, this paper proposes the use of Natural Language Processing (NLP) as an engine to digitize the legal text of the RA. The NLP engine analyzes the different articles and sub-articles of the RA determining the existence of variables, variations, standard clauses and customized texts in the text.

@@

Both in the scientific literature and in business environments there are important approaches to RA digitalization. Thus, the reference \cite{b5} proposes a dynamic RA between the Local 5G Operator and the MNO. The interaction between the two entities takes place through an Ethereum based platform. A second approach focuses uniquely on the billing of the services obtained as a result of the RA \cite{b6}. This agreement is incorporated as part of a smart contract so the work contributes significantly to the digitization process of the agreement, allowing for a faster, more seamless process in which payments can be requested and obtained quickly due to less need for manual intervention. The contextualization of this system in the business environment is proposed by important MNOs such as Telefonica, Deutsche Telekom and Vodafone which use blockchain for Roaming settlement within the framework of the RA between the parties \cite{b7}. However, these contributions are focused from a RA implementation perspective rather than the negotiation context of drafting the RA. Similarly, the scientific literature addresses text processing systems based on nlp techniques in domains such as healthcare and the judiciary. Thus, the reference \cite{b8} applies NLP-based processing techniques for information retrieval from spreadsheets and describes technologies for storing and retrieving database information. NLP techniques such as sentence tokenization, word tokenization, removing stopwords and lemmatization are part of the parsing stage of the work. In addition, the reference \cite{b9} addresses the process of digitization in the judicial sectors from archives of court records for which the authors have designed a textual analysis tool that includes grammatical analysis of documents in English based on NLP techniques. This linguistic analysis attempts to find the appropriate meaning of terms within a document. Finally, authors of reference \cite{b10} propose a model for implementing sentimental analysis using Amazon Comprehend. This system performs an audio-to-text transcription and then performs the processing of the obtained text. Although these studies are part of related work, for example, by integrating useful tools such as Amazon Comprehend or detailing the use of techniques such as tokenization, the scientific literature does not address scenarios for the telecom field and even less in the context of negotiating the RA drafting. Therefore, we can affirm that our work represents a topic with a high degree of novelty.

>>>>

\section{Introduction}
The roaming service maintains the persistent connectivity of subscribers in different networks and locations. Roaming describes the capability of a subscriber to access mobile services offered by the visited public mobile network (VPMN) through the home public mobile network (HPMN), when roaming outside the coverage range of the HPMN \cite{b1}. However, before ensuring persistent connectivity the Mobile Network Operators (MNOs) must reach an agreement regarding the technical, commercial and legal relationships known as the Roaming Agreement (RA).

In order to standardize technical, commercial and legal aspects of RA, the GSM Association broadly outlines the content of such RA in standardized form for its members \cite{b2}. Reference \cite{b3} provides a list of the most commonly used GSMA standards, which are summarized bellow: (1) AA.12 constitutes a standard GSMA or Permanent Reference Document; (2) AA.13 contains the common annexes with operational information (e.g., information on tap file, billing data, settlement procedure, customer care, fraud, etc.); (3) AA.14 involves the individual annexes containing information about the operator (e.g., contact details of the roaming team, fraud team, IREG team, TADIG team, etc.) and (4) AA.19 is an addendum to the international RA to determine specific properties such as charging, billing and accounting for a specific scenario such as SMS interworking. Thus, the contractual relationship between MNOs depends on the drafting of an RA between the parties.

While it is true that it is not mandatory to follow the standards proposed by GSMA, according to authoritative voices in the field of negotiating RA drafting, most MNOs follow them strictly \cite{b4}. Therefore, a first point to consider in the RA drafting is how far it is deviated from the GSMA's proposed standards. Thus, during the drafting process of the agreement, the parties should analyze the sub-articles contained in the GSMA standard templates to determine whether:

\begin{enumerate}
\item Specify the value of certain variables that are found in a certain text, such as dates, names of entities, amounts and others.

\item Leave an article/sub-article as found in the template thereby establishing a standard clause.

@@

@@

However, a successful RA drafting goes through a complex negotiation process in which, currently the parties, i.e. the Mobile Network Operators (MNOs), still use asynchronous flows such as email or even regular mail for information exchange. Since these processes lack transparency, which can result in the violation of the RA by MNOs, it is necessary to provide a transparent digitization system for RA drafting negotiations. For this reason, this paper proposes the use of Natural Language Processing (NLP) as an engine to digitize the legal text as a starting point of a RA transparent drafting process. The NLP engine analyzes the different articles and sub-articles of the RA determining the existence of variables, variations, standard clauses and customized texts in the text. For this purpose, on the one hand, NLP techniques such as Named Entity Recognition (NER) and Part of Speech (POS) are applied from an unstructured data information discovery tools such as Amazon Comprehend and on the other hand, a comprehensive comparison between texts is established based on similarity determination techniques. Both techniques are integrated as part of the development of an unstructured text processing tool that integrates an specific methodology for the use case, i.e., a transparent digitization of roaming agreements.

@@

Both in the scientific literature and in business environments there are important approaches to RA digitalization. Thus, the reference \cite{b5} proposes a dynamic RA between the Local 5G Operator and the MNO. The interaction between the two entities takes place through an Ethereum based platform. A second approach focuses uniquely on the billing of the services obtained as a result of the RA \cite{b6}. This agreement is incorporated as part of a smart contract so the work contributes significantly to the digitization process of the agreement, allowing for a faster, more seamless process in which payments can be requested and obtained quickly due to less need for manual intervention. The contextualization of this system in the business environment is proposed by important MNOs such as Telefonica, Deutsche Telekom and Vodafone which use blockchain for Roaming settlement within the framework of the RA between the parties \cite{b7}. However, these contributions are focused from a RA technical perspective rather than the context of a transparent digitization to enhance the negotiation process for the effective drafting of the roaming agreement.

Additionally, the scientific literature addresses text processing systems based on nlp techniques in domains such as judiciary. Thus, the reference \cite{b9} addresses the process of digitization in the judicial sectors from archives of court records for which the authors have designed a textual analysis tool that includes grammatical analysis of documents in English based on NLP techniques. This linguistic analysis attempts to find the appropriate meaning of terms within a document. In addition, the reference \cite{b8} applies NLP-based processing techniques for information retrieval from spreadsheets and describes technologies for storing and retrieving database information. NLP techniques such as sentence tokenization, word tokenization, removing stopwords and lemmatization are part of the parsing stage of the work. Finally, authors of reference \cite{b10} propose a model for implementing sentimental analysis using Amazon Comprehend. This system performs an audio-to-text transcription and then performs the processing of the obtained text. Although these studies  constitute a relevant part of related work, e.g., by integrating useful tools such as Amazon Comprehend or detailing the use of techniques such as tokenization, the scientific literature does not address scenarios for the telecom field and even less in the context of a transparent digitization of the roaming agreement. Therefore, we can affirm that our work introduces a topic with a high degree of novelty.
